Errors in Landcover Data Limit Our Understanding of Global Change

### 2015-12-27 paper/main.tex
Edited tex class to drop PNAS from footers

%% BASIC CLASS FILE
\documentclass{pnastwo}

@@

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}
%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

@@

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

%%%Newly updated.
%%% If significance statement need, then can use the below command otherwise just delete it.
\significancetext{Remote sensing-derived landcover maps underpin much research into global environmental change, particularly in the most rapidly developing regions. These maps often contain substantial error, yet inadequate validation data makes it impossible to fully quantify map errors and how they affect our understanding of global change processes. Using a unique, high quality reference map of cropland distribution, this study comprehensively assesses landcover map bias and accuracy in a major agricultural region of sub-Saharan Africa, finding that map errors are strongly correlated with the landcover density, and can propagate substantial errors in downstream global change analyses. Users of landcover maps should select later generation products and aggregate to appropriate resolutions to avoid misleading insights and policies related to global change. }

>>>>

%% BASIC CLASS FILE
\documentclass{pnastwo2}

@@

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}
%%%%%%%%%%%%
%% For PNAS Only:
%\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

@@

%\contributor{Submitted to Proceedings of the National Academy of Sciences
%of the United States of America}

%%%Newly updated.
%%% If significance statement need, then can use the below command otherwise just delete it.
%\significancetext{Remote sensing-derived landcover maps underpin much research into global environmental change, particularly in the most rapidly developing regions. These maps often contain substantial error, yet inadequate validation data makes it impossible to fully quantify map errors and how they affect our understanding of global change processes. Using a unique, high quality reference map of cropland distribution, this study comprehensively assesses landcover map bias and accuracy in a major agricultural region of sub-Saharan Africa, finding that map errors are strongly correlated with the landcover density, and can propagate substantial errors in downstream global change analyses. Users of landcover maps should select later generation products and aggregate to appropriate resolutions to avoid misleading insights and policies related to global change. }
